---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pfGO

<!-- badges: start -->
<!-- badges: end -->

The goal of pfGO is to package handy functions and datasets specifically enabling *Plasmodium falciparum* functional enrichment analyses. pfGO acts as a wrapper around the topGO package for much of its enrichment functionality, while also providing several functions for incorporating latest gene-ontology and functional annotations.

pfGO enables chaining together many parallel enrichment-analyses at once, generating thorough logs and outputs supporting reproducible analyses.


## Installation

You can install the development version of pfGO from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("oberstal/pfGO")
```

See individual functions/data objects for further documentation. E.g.:
``` r 
?run.topGO.meta
?Pfal_geneID2GO

# for all available functions/data:
?pfGO
  # then scroll to the bottom and click the "index" link.
```



## Example

This is a basic example demonstrating how to run an enrichment analysis:

```{r message=FALSE, warning=FALSE}
library(pfGO)
```

```{r example, warning=FALSE}
# load included pf GO database and example-data to be tested for functional enrichment
data("Pfal_geneID2GO")
data("exampleMydf")

# run the topGO pipeline on all experimental categories of interest from exampleMydf
run.topGO.meta(mydf = exampleMydf, geneID2GO = Pfal_geneID2GO, pval = 0.05)

```
